Contention Management for 5G

### 2017-05-16 article/article.tex
debut waiting time

      In this section, we consider graphs with a very simple topology that we call the {\bf star topology}. 
      First, for each arc $(u,v)$, there is also an arc $(v,u)$ with the same weight.
      Moreover, there is a special arc, the central arc, which is shared by all routes.
      All routes consist from an arc from its source to the central source node, denoted by {\bf $c_s$},
      then the central arc to {\bf $c_t$}, the central target node, and an arc to its target. In addition to those central nodes, there are two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$, of cardinality $n$ and ${\cal C}$ a symmetric assignment from $S$ to $T$. 
      The routes are the directed paths of the form $s_i,c_s,c_t,t_i$ and $t_i,c_t,c_s,s_i$.

@@

	  We now consider waiting times. The weights on links from sources to $c_s$ are now relevant because the goal is to minimize $MT({\cal M})$, with ${\cal M}$ the $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$.
	  To build such a $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, we must choose the offsets $m_{s_i}$ and $m_{t_i}$, such that there is no $PT(s)$ greater than a given $T_{max}$.
	  As a reminder, $ PT(s)=\lambda(r_s)+ w_s+\lambda(r_{t_i})$.
     \subsubsection{LSG}

@@

On $c_t$, the policy is the following one, after setting the clock to 0:
\begin{enumerate}
 \item To be eligible, a job needs to be able to come back on the switch at the current clock (if clock = 0, take the first message able to come back).
 \item Between the eligible jobs, schedule first the one which has the lowest deadline.
 \item Repeat until all the messages had been scheduled.
\end{enumerate}

For any route i, the deadline correspond to $m_{s_i} + T_{max}$.

\begin{algorithm}[H]
\caption{LSG}
\begin{algorithmic}
\REQUIRE routage graph ${\cal R_{\cal C}}$, period $P$, packet size $\tau$
\ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$
\STATE clock $\leftarrow$ 0
\FORALL{route i in $r_{s_i}$ from the longest to the shortest }
\STATE  $m_{s_i} \leftarrow$ clock
\STATE clock $\leftarrow$ clock + $\tau$
\ENDFOR
\STATE clock $\leftarrow$ 0
\STATE take i such that $r_{\cal C(s_i)}$ is the first route to come back in sources switch
\STATE $m_{\cal C(s_i)} \leftarrow $ clock;
\STATE clock $\leftarrow$ $t(c_t,r_{\cal C(s_i)})$ + $\tau$
\WHILE{there is a route which has not been scheduled}
\STATE take i such that $r_{\cal C(s_i)}$ is the eligible route.
\STATE $m_{\cal C(s_i)} \leftarrow $ clock - $t(c_t,r_{\cal C(s_i)})$;
\STATE clock $\leftarrow$ clock + $\tau$

\ENDWHILE

\end{algorithmic}
\end{algorithm}

	\paragraph{Analysis}

One of the closest approach to real networks is the case in which all the weight on the arcs going from $c_t$ to targets are the, this algorithm gives an optimal solution. Indeed, all the same weight can be simplified by 0, thus the scheduling in the forward and backward period is the same, that is, all message following each others, so the period is minimal : $n.\tau$, where $n$ is the number of couples $(s,{\cal C}(s))$. Furthermore, all the waiting times are set to 0 i.e. $w_i = 0,\forall i \in n$, thus, $MT({\cal M})$ is equal to twice the longer delay of the routes, that is not alterable.

@@

     \subsubsection{Results}
	 \paragraph{Random}
	 \paragraph{Distributions}

@@

Open questions. Can we improve the results if:
\begin{itemize}
 \item The routes are smaller than the size of a message. 
\item The routes are smaller than the period.
\item The largest difference between two routes is smallest than one of these parameters
\end{itemize}

 On a general graph:

\begin{itemize}
\item The routing is coherent
 \item The graph is symmetric
\end{itemize}

>>>>

      In this paper, we consider graphs with a very simple topology that we call the {\bf star topology}. 
      First, for each arc $(u,v)$, there is also an arc $(v,u)$ with the same weight.
      Moreover, there is a special arc, the central arc, which is shared by all routes.
      All routes consist from an arc from its source to the central source node, denoted by {\bf $c_s$},
      then the central arc to {\bf $c_t$}, the central target node, and an arc to its target. In addition to those central nodes, there are two sets of vertices, $S=\{s_0,...,s_{n-1}\}$ and $T=\{t_0,...,t_{n-1}\}$, of cardinality $n$ and ${\cal C}$ a symmetric assignment from $S$ to $T$. 
      The routes are the directed paths of the form $s_i,c_s,c_t,t_i$ and $t_i,c_t,c_s,s_i$.

@@

	  In the previous section, we described some algorithm to solve an easier version of PALL, in which there is no waiting times. As we just conclude, this problem cannot be solved when the period is too small. The C-RAN context gives us a fixed period, thus, some topologies with a lot of routes might be impossible to schedule with the previous algorithms. We propose to allow some message to wait in the target vertices (BBU), with the aim of giving an higher degree of freedom for the scheduling. In this section, the waiting times $w_i$ are not necessarily null anymore. Thus, $MT({\cal M})$ might be superior to $T_{max}$ and it is necessary to minimize $MT({\cal M})$.

% 	  We now consider waiting times. The weights on links from sources to $c_s$ are now relevant because the goal is to minimize $MT({\cal M})$, with ${\cal M}$ the $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$.
% 	  To build such a $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, we must choose the offsets $m_{s_i}$ and $m_{t_i}$, such that there is no $PT(s)$ greater than a given $T_{max}$.
% 	  As a reminder, $ PT(s)=\lambda(r_s)+ w_s+\lambda(r_{t_i})$.

     \subsubsection{A first approach}

@@

      On $c_t$, the policy is the following one, after setting the clock to 0:
      \begin{enumerate}
      \item To be eligible, a message needs to be able to come back on $c_t$ at the current clock (if clock = 0, take the first message able to come back).
      \item Between the eligible messages, schedule first the one which has the lowest deadline.
      \item Repeat until all the messages had been scheduled.
      \end{enumerate}

      For any route i, the deadline correspond to $m_{s_i} + T_{max}-t(c_s,r_{s_i})$. This deadline corresponds to the latest date at which a message is able to quit the target switch without exceed $T_{max}$.
% 
% \begin{algorithm}[H]
% \caption{Longest Shortest Greedy (LSG)}
% \begin{algorithmic}
% \REQUIRE routage graph ${\cal R_{\cal C}}$, period $P$, packet size $\tau$
% \ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$
% \STATE clock $\leftarrow$ 0
% \FORALL{route i in $r_{s_i}$ from the longest to the shortest }
% \STATE  $m_{s_i} \leftarrow$ clock
% \STATE clock $\leftarrow$ clock + $\tau$
% \ENDFOR
% \STATE clock $\leftarrow$ 0
% \STATE take i such that $r_{\cal C(s_i)}$ is the first route to come back in sources switch
% \STATE $m_{\cal C(s_i)} \leftarrow $ clock;
% \STATE clock $\leftarrow$ $t(c_t,r_{\cal C(s_i)})$ + $\tau$
% \WHILE{there is a route which has not been scheduled}
% \STATE take i such that $r_{\cal C(s_i)}$ is the eligible route.
% \STATE $m_{\cal C(s_i)} \leftarrow $ clock - $t(c_t,r_{\cal C(s_i)})$;
% \STATE clock $\leftarrow$ clock + $\tau$
% 
% \ENDWHILE
% 
% \end{algorithmic}
% \end{algorithm}
\todo{ecrire l'algo}

	\paragraph{Particular case corresponding to C-RAN}

	One of the closest approach to real networks is the case in which all the weight on the arcs going from $c_t$ to targets are the, this algorithm gives an optimal solution. Indeed, all the same weight can be simplified by 0, thus the scheduling in the forward and backward period is the same, that is, all message following each others, so the period is minimal : $n.\tau$, where $n$ is the number of routes. Furthermore, all the waiting times are set to 0 i.e. $w_i = 0,\forall i \in n$, thus, $MT({\cal M})$ is equal to twice the longer delay of the routes, that is not alterable.

@@

     \subsubsection{Sending order}

     \subsubsection{A better Algorithm : periodicity}

     \subsubsection{Another better Algorithm : $T_{MAX}$}

     \subsubsection{Mix : Simons periodic}

@@
